### 2024-02-05 ms.qmd
Updates

## Introduction
Behavioural flexibility, the ability to adjust the behaviour in response to internal or external changes in an adaptive way by, e.g., problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. Indeed, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural]. According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation [**REFS**]. Since behavioural flexibility can be affected by early environment [@jonson1976effect; @lui2017chronic], it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations, with a consequent impact on invasion success. Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and whether their susceptibility to the early environment can predict the success of invasive species.  
Here, we are particularly interested in the interactive contribution of prenatal temperature and Glucocorticoids (GCs). There are several reasons why we believe these two aspects are salient for studying behavioural flexibility in the context of invasion ecology. First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments. Furthermore, Gcs are one of the mechanisms mediating vertebrates’ response to changes in temperature that, at the same time, can have direct effects on animals' physiology and behaviour [@Crino_2023]. Secondly, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic]. For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect]. In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].

MODEL SPECIES AND POPULATIONS
To do so, we employed as our model species the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L. delicata_ has been succesful in colonising different areas around the globe (**REFS**). Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L. delicata_ (**REFS**), and are likely key for its invassive success (**REFS**).

HYPOTHESES
Here, we aim to study the effects of prenatal environment on behavioural flexibility in the invassion ecology context.

@@

>>>>

## Introduction
Behavioural flexibility, the ability to adjust the behaviour adaptively in response to internal or external by, e.g., problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. Indeed, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural]. According to the adaptive flexibility hypothesis, behavioural flexibility can be more relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that, nonetheless, can involve more than one generation. If behavioural flexibility is adaptive in these different stages, both this trait and the underlining mechanisms are expected to persist through generations in succesful invaders. For example, relative brain size is a good predictor of behavioural flexibility and invasive success in mammals [@sol2008brain], birds [@sol2000behavioural; @sol2002behavioural], reptiles, and amphibians [@amiel_effects_2017]. Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success. Therefore, we consider important to investigate the effect of developmental conditions on behavioural flexibility and whether their susceptibility to the early environment can predict the success of invasive species.  
In this scenario, we consider prenatal GCs and thermal environment to be salient factors in the study of behavioural flexibility within the context of invasion biology for several reasons. First, GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments. Furthermore, Gcs are one of the mechanisms mediating vertebrates’ response to changes in temperature that, at the same time, can have direct effects on animals' physiology and behaviour [@Crino_2023]. Secondly, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic]. For instance, young Sprague-Dawley rats treated with Corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impariments with offspring behavoural flexibility [@jonson1976effect]. In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004], an aspect that is considered essential in succesful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].
Here, we studied the interactive contribution of prenatal temperature and Glucocorticoids (GCs) on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L. delicata_ has been succesful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI]. Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L. delicata_, and are likely key for its invassive success [@chapple_know_2011; @chapple2012can; @bezzina2014does]. However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remains unknown. To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, and then subjected the juveniles to a reversal learning task as a measure of behavioural flexibility [@brown2010behavioral; @szabo2020can]. We predicted that _L. delicata_ would, on average, perform more proficiently in the task that _L. guichenoti_. We also anticipated prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L. guichenoti_ would be more impacted by the prenatal environment than _L. delicata_. Regarding the directionality of the treatments, high prenatal temperatures are considered to improve performance in cognitive tasks in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], so we expected those incubated at higher temperatures to perform better in the reversal task. On the other hand, we expected that prenatal CORT would impair the performance of the lizards in the task, as it has been shown in other species [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic].

@@

**Our results suggest that prenatal CORT and temperature do not affect the behavioural flexibility of _L. delicata_ and _L. guichenoti_. We did not find any significant differences between treatments in the reversal task, and when we compared the estimated slopes between species. This is in contrast with our predictions, as we expected that _L. guichenoti_ would be more impacted by the prenatal environment than _L. delicata_. We also expected that prenatal CORT would impair the performance of the lizards in the task, and that higher temperatures would improve it. However, we did not find any evidence of this.

They learn on average, as shown by positive slopes that do not vary when only those "superperformers" are employed in the analyses.

Why no effect of treatment? 
    What is expected from CORT? Other studeis showing no effects or the opposite: @szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016. Multiple factors may affect this results, including the dose of CORT, the time of exposure, and the species. Reversal?? Check @lui2017chronic and @jonson1976effect.

    What is expected from temperature? Other studies showing no effects or the opposite: @abayarathna_effects_2020; @dayananda. But these studies are in other species and with temperatures above the natural range. None of them reversal?? Only reversal done with criterion, so cold were not tested

    Selective sieve? No effects because is too simple?

Why no differences between species?
    Other papers finding no effects in learning: @bezzina2014does. Here they did not learn at all, too complex? Related with absence of treatment effects?

    No differences in treatment effects

Conclusions (sum up the discussion)**
